Volatility Metric to Detect Anomalies in Source Code Repositories

### 2020-04-19 paper/article.tex
more

In order to demonstrate how the metric works we applied it to
\thetotalrepos{} public Java repositories from GitHub and analyzed
its impact on a two other characteristics of each repository:
the number of files in a repository and the size of it in bytes.
Larger repositories shown larger values of the volatility.

@@

In this paper, we use several terms regarding version control systems and
software metrics. The type of metric we are proposing belongs to the family
of source code change metrics, which analyze the history
of changes in a source code repository~\citep{fentonsoftware,choudhary2018}.
A \emph{change} in a version control system, such as Git, is an individual
modification to the source code file made by a software developer locally
on his/her machine and then \emph{committed} to the repository.

@@

Code churn is one of the simplest metric in the family, which counts
all lines being modified (added, edited, and deleted) during
the entire lifetime of a project~\citep{munson1998}. It was demonstrated
by~\citet{shin2010} how code churn, together with complexity and other
developer activity metrics, is related to software vulnerabilities.
Yet another simple metrict from the family is
the number of changes being made to a particular file, class, method
or line of code is yet another simple metric, used for example by~\citet{demeyer2000}
in order to analyze the effect of refactorings.

@@

To our knowledge, the metric introduced in this research has never been
suggested.

>>>>

In order to demonstrate how the metric works we applied it to
\thetotalrepos{} public Java repositories from GitHub and analyzed
its impact on a two other characteristics of each repository:
the number of files in a repository and the size of it in bytes.
Larger repositories shown larger values of the metric.

@@

In this paper, we use several terms regarding version control systems and
software metrics. The type of metric we are proposing belongs to the family
of \emph{source code change metrics}, which analyze the history
of changes in a source code repository~\citep{fentonsoftware,choudhary2018}.
A \emph{change} in a version control system, such as Git, is an atomic
modification to the source code file made by a software developer locally
on his/her machine and then \emph{committed} to the repository.

@@

Code churn is one of the simplest metric in the family, which counts
all lines being modified (added, edited, and deleted) during
the entire lifetime of a project~\citep{munson1998}. It was demonstrated
by~\citet{shin2010} how code churn, together with complexity and other
developer activity metrics, is related to software vulnerabilities. There
are modifications of code churn, for example taking into accout socio-technical
aspect of the metric, as suggested by~\citet{meneely2012}.

Yet another simple metrict from the family is
the number of changes being made to a particular file, class, method
or line of code is yet another simple metric, used for example by~\citet{demeyer2000}
in order to analyze the effect of refactorings.

@@

To our knowledge, the metrics introduced in this research, in order
to detect anomalies in source code repository maintenance, has never been
suggested.
